# Appendix {#appendix}

## Simulated Data Creation {#sec:sim-data}

Below is the code used to create the simulated data that will be used to create the example SGBA seen throughout the rest of this example analysis.

```{r sim-data-creation}
# load libraries ----------------------------------------------------------
library(tidyverse)

# set seed for predictability
set.seed(42, kind = "Mersenne-Twister")

# write simulation functions ----------------------------------------------

# function for simulating bimodal gender variables
binom_bounded <- function(
    n, prop, mean1, sd1, mean2, sd2, lim_low = -Inf, lim_up = Inf, round
    ){
  # error checking
  if(prop > 1 || prop< 0){stop("binomial proportion should be between 0 and 1")}
  if(n < 1){stop("n must be greater than or equal to 1")}
  if(sd1 < 0 || sd2 < 0){stop("standard deviations must be non-negative")}
  # create index
  index <- rbinom(n, size = 1, prob = prop)
  # simulate each peak using a bounded `rnorm()`
  binom_sim1 <- index * qnorm(
    runif(
      n, pnorm(lim_low, mean1, sd1), pnorm(lim_up, mean1, sd1)
      ), 
    mean1, sd1)
  binom_sim0 <- (1 - index) * qnorm(
    runif(
      n, pnorm(lim_low, mean2, sd2), pnorm(lim_up, mean2, sd2)
      ), 
    mean2, sd2)
  binom_sim <- binom_sim0 + binom_sim1
  binom_sim <- round(binom_sim, round)
  binom_sim
}


# function for simulating Likert/ordinal outcome variable
ordinal_sim <- function(
    n, mean, sd, lim_low = -Inf, lim_up = Inf
    ){
  ord_sim <- qnorm(
    runif(
      n, pnorm(lim_low, mean, sd), pnorm(lim_up, mean, sd)
      ),
    mean, sd)
  ord_sim <- round(ord_sim, 0)
  ord_sim
}


# simulate SGBA-5 data with n of 30 -------------------------------------

# biological sex: categorical (female, intersex, male)
bio_sex <- factor(
  sample(c('Female', 'Male'), 30, replace=TRUE, prob=c(0.6, 0.4)),
  )

# gender identity: ordered (0 [feminine] to 100 [masculine])
gen_id <- binom_bounded(
  n = 30, prop = 0.6, mean1 = 20, sd1 = 20, mean2 = 85, sd2 = 15, lim_low = 0,
  lim_up = 100, round = 0
)

# gender role: ordered (0 [feminine] to 100 [masculine])
gen_role <- binom_bounded(
  n = 30, prop = 0.6, mean1 = 25, sd1 = 20, mean2 = 80, sd2 = 20, lim_low = 0,
  lim_up = 100, round = 0
)


# simulate example positive outcome data with n of 30 -----------------------

## simulated numerical outcome: --------------------------------------------

# by sex: males (mean = 12, SD = 3), females (mean = 4, sd = 2)
outcome_num_pos_m <- rnorm(n = 16, mean = 12, sd = 3)
outcome_num_pos_f <- rnorm(n = 14, mean = 4, sd = 2)
outcome_num_pos_sex <- c(outcome_num_pos_f, outcome_num_pos_m)

# by g_id: high (mean = 12, SD = 3), low (mean = 4, sd = 2)
outcome_num_pos_gid_high <- rnorm(n = 15, mean = 12, sd = 3)
outcome_num_pos_gid_low <- rnorm(n = 15, mean = 4, sd = 2)
outcome_num_pos_gid <- c(outcome_num_pos_gid_high, outcome_num_pos_gid_low)

# by g_role: high (mean = 12, SD = 3), low (mean = 4, sd = 2)
outcome_num_pos_grol_high <- rnorm(n = 12, mean = 12, sd = 3)
outcome_num_pos_grol_low <- rnorm(n = 18, mean = 7, sd = 2)
outcome_num_pos_grol <- c(outcome_num_pos_grol_high, outcome_num_pos_grol_low)


## simulated Likert outcome: ---------------------------------------------

# by sex males (mean = 2, SD = 1), females (mean = 5, sd = 2)
outcome_ord_pos_m <- ordinal_sim(
  n = 16, mean = 2, sd = 1, lim_low = 1, lim_up = 7
)
outcome_ord_pos_f <- ordinal_sim(
  n = 14, mean = 5, sd = 1, lim_low = 1, lim_up = 7
)
outcome_ord_pos_sex <- c(outcome_ord_pos_f, outcome_ord_pos_m) %>%
  factor(., levels = c(1,2,3,4,5,6,7), ordered = TRUE)


# by g_id: high (mean = 5, SD = 2), low (mean = 1, sd = 2)
outcome_ord_pos_high <- ordinal_sim(
  n = 15, mean = 5, sd = 2, lim_low = 1, lim_up = 7
)
outcome_ord_pos_low <- ordinal_sim(
  n = 15, mean = 1, sd = 2, lim_low = 1, lim_up = 7
)
outcome_ord_pos_gid <- c(outcome_ord_pos_high, outcome_ord_pos_low) %>%
  factor(., levels = c(1,2,3,4,5,6,7), ordered = TRUE)


# by g_role: high (mean = 5, SD = 2), low (mean = 1, sd = 2)
outcome_ord_pos_high <- ordinal_sim(
  n = 12, mean = 5, sd = 2, lim_low = 1, lim_up = 7
)
outcome_ord_pos_low <- ordinal_sim(
  n = 18, mean = 1, sd = 2, lim_low = 1, lim_up = 7
)
outcome_ord_pos_grol <- c(outcome_ord_pos_high, outcome_ord_pos_low) %>%
  factor(., levels = c(1,2,3,4,5,6,7), ordered = TRUE)


## simulated binary outcome: -----------------------------------------------

# by sex males (yes = .2, no = .8), females (yes = .8, no = .2)
outcome_bin_pos_m <- sample(
  c('yes','no'), 16, replace = TRUE, prob = c(.2, .8)
)
outcome_bin_pos_f <- sample(
  c('yes','no'), 14, replace = TRUE, prob = c(.8, .2)
)
outcome_bin_pos_sex <- append(outcome_bin_pos_f, outcome_bin_pos_m) %>%
  factor()


# by g_id: high (yes = .4, no = .6), low (yes = .8, no = .2)
outcome_bin_pos_high <- sample(
  c('yes','no'), 15, replace = TRUE, prob = c(.4, .6)
)
outcome_bin_pos_low <- sample(
  c('yes','no'), 15, replace = TRUE, prob = c(.8, .2)
)
outcome_bin_pos_gid <- append(outcome_bin_pos_high, outcome_bin_pos_low) %>%
  factor()


# by g_rol: high (yes = .3, no = .5), low (yes = .8, no = .2)
outcome_bin_pos_high <- sample(
  c('yes','no'), 12, replace = TRUE, prob = c(.3, .7)
)
outcome_bin_pos_low <- sample(
  c('yes','no'), 18, replace = TRUE, prob = c(.8, .2)
)
outcome_bin_pos_grol <- append(outcome_bin_pos_high, outcome_bin_pos_low) %>%
  factor()


# simulate example negative outcome data with n of 30 -----------------------

# simulated numerical outcome: continuous (mean = 10, SD = 3)
outcome_num_neg <- rnorm(n = 30, mean = 10, sd = 3)

# simulated Likert outcome: 7-point Likert scale (mean = 4, SD = 2)
outcome_ord_neg <- ordinal_sim(
  n = 30, mean = 4, sd = 2, lim_low = 1, lim_up = 7
)

# simulated binary outcome: categorical (yes, no)
outcome_bin_neg <- factor(
  sample(c('yes','no'), 30, replace = TRUE, prob = c(0.67, 0.33))
)


# create example data frame -----------------------------------------------

# combine into dataframe
sim_data <- tibble(
  bio_sex, gen_id, gen_role, #outcome_bin_pos, 
  outcome_num_neg, outcome_ord_neg, outcome_bin_neg
  ) %>% arrange(., bio_sex) %>% 
  cbind(., outcome_num_pos_sex) %>%
  cbind(., outcome_ord_pos_sex) %>%
  cbind(., outcome_bin_pos_sex) %>%
  arrange(., gen_id) %>% 
  cbind(., outcome_num_pos_gid) %>% 
  cbind(., outcome_ord_pos_gid) %>%
  cbind(., outcome_bin_pos_gid) %>%
  arrange(., gen_role) %>% 
  cbind(., outcome_num_pos_grol) %>% 
  cbind(., outcome_ord_pos_grol) %>%
  cbind(., outcome_bin_pos_grol)


# save simulated df
write_csv(sim_data, file = "sim-data.csv")

```

### Session Info for Data Creation

```{r session-info}
sessioninfo::session_info(pkgs = "loaded")
```

## Ch. 3 Descriptive Analysis {#sec:rcode-ch3}

### Ch. 3 Set Up 

```{r eval=FALSE}
# load libraries and simulated data ---------------------------------------
library(tidyverse)
library(ggpubr)

# set seed for reproducibility
set.seed(42)

# load data set (from RDS if using previous script to simulate the data)
sim_data <- read_csv(file = "sim-data.csv")

# default density plots and scale function ----------------------------------
plot_dens_2D <- function(data, x, y){
  plot <- ggplot(data = data, aes(x = x, y = y)) + 
    geom_density_2d_filled(aes(fill = after_stat(level)),
                           bins = 9, contour_var = 'ndensity') +
    scale_fill_brewer(palette = 16, direction = 1, 
                      labels = c('Low', '', '', '','','','','', 'High')) +
    guides(fill = guide_legend(title = 'Density of Occurences', 
                               direction = 'horizontal', nrow = 1, 
                               label.position = 'bottom'))
  plot
}
```

### Figure 3.1

```{r eval=FALSE}
# biological sex bar plot
ggplot(sim_data, aes(x = bio_sex)) +
  geom_bar(aes(fill = bio_sex), show.legend = F) + 
  labs(title = 'Barplot of Simulated Biological Sex') +
  ylab('Count') + xlab('Biological Sex') +
  theme_classic()
```

### Figure 3.2

```{r eval=FALSE}
# gender identity density plot
ggplot(sim_data, aes(x = gen_id)) +
  geom_density(alpha=.5, fill = 'forestgreen', colour = 'black') +
  labs(title = 'Density plot of Simulated\nGender Identity Responses') +
  ylab('Density') + xlab('Feminine - Masculine Continuum') +
  theme_classic() +
  theme(
    legend.position = 'none',
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank()
  )

# gender role density plot
ggplot(sim_data, aes(x = gen_role)) +
  geom_density(alpha=.5, fill = 'purple2', colour = 'black') +
  labs(title = 'Densityplot of Simulated\nGender Role Responses') +
  ylab('Density') + xlab('Feminine - Masculine Continuum') +
  theme_classic() +
  theme(
    legend.position = 'none',
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank()
  )
```

## Ch. 4 SGBA of a Continuous Variable {#sec:rcode-ch4}

### Ch. 4 Set Up

```{r eval=FALSE}
# load libraries and simulated data ---------------------------------------
library(tidyverse)
library(ggpubr)

# set seed for reproducibility
set.seed(42)

# load data set (from RDS if using previous script to simulate the data)
sim_data <- read_csv(file = "sim-data.csv")

# default density plots and scale function ----------------------------------
plot_dens_2D <- function(data, x, y){
  plot <- ggplot(data = data, aes(x = x, y = y)) + 
    geom_density_2d_filled(aes(fill = after_stat(level)),
                           bins = 9, contour_var = 'ndensity') +
    scale_fill_brewer(palette = 16, direction = 1, 
                      labels = c('Low', '', '', '','','','','', 'High')) +
    guides(fill = guide_legend(title = 'Density of Occurences', 
                               direction = 'horizontal', nrow = 1, 
                               label.position = 'bottom'))
  plot
}
```

### Figure 4.1

```{r eval=FALSE}
# biological sex bar plot - interaction
ggplot(sim_data, aes(x = outcome_num_pos_sex, fill = bio_sex)) + 
  geom_density(alpha = 0.7) +
  scale_fill_manual(values = c('forestgreen', 'skyblue')) +
  labs(
    title = 'Interaction example',
    subtitle = 'Density plot of continuous \noutcome and biological sex (n=30)'
    ) +
  xlab('Continuous Outcome') + 
  ylab('Response Density') +
  theme_classic() +
  theme(legend.position = 'bottom')

# biological sex bar plot - no interaction
ggplot(sim_data, aes(x = outcome_num_neg, fill = bio_sex)) + 
  geom_density(alpha = 0.7) +
  scale_fill_manual(values = c('forestgreen', 'skyblue')) +
  labs(
    title = 'No interaction example',
    subtitle = 'Density plot of continuous \noutcome and biological sex (n=30)'
    ) +
  xlab('Continuous Outcome') + 
  ylab('Response Density') +
  theme_classic() +
  theme(legend.position = 'bottom')
```

### Table 4.1

```{r eval=FALSE}
# summary stats
pos_cont_sex_sum <- sim_data %>% group_by(bio_sex) %>% 
  summarise(
    n = n(), 
    `mean continuous` = round(mean(outcome_num_pos_sex),1),
    `SD continuous` = round(sd(outcome_num_pos_sex),2),
    `median continuous` = round(median(outcome_num_pos_sex),0),
    `IQR continuous` = round(IQR(outcome_num_pos_sex),)
  ) %>% 
  rename(`biological sex` = bio_sex) 

knitr::kable(pos_cont_sex_sum, booktabs = TRUE, caption = "Interation example summary statisitics: Continuous outcome and biological sex")
```

### Table 4.2

```{r eval=FALSE}
neg_cont_sex_sum <- sim_data %>% group_by(bio_sex) %>% 
  summarise(
    n = n(), 
    `mean continuous` = round(mean(outcome_num_neg),1),
    `SD continuous` = round(sd(outcome_num_neg),2),
    `median continuous` = round(median(outcome_num_neg),0),
    `IQR continuous` = round(IQR(outcome_num_neg),)
  ) %>% 
  rename(`biological sex` = bio_sex) 

knitr::kable(neg_cont_sex_sum, booktabs = TRUE, caption = "No interation example summary statisitics: Continuous outcome and biological sex")
```

### Table 4.3

```{r eval=FALSE}
# t-tests
con_sex_ttest_neg <- t.test(outcome_num_neg ~ bio_sex, data = sim_data)
con_sex_ttest_pos <- t.test(outcome_num_pos_sex ~ bio_sex, data = sim_data)

# example of collected data
con_sex_tab <- tibble(
  "Example" = c("Interaction", "No interaction"),
  "Test" = c("Welch's t-test", "Welch's t-test"),
  "T-score" = c(
    round(con_sex_ttest_pos$statistic,2),
    round(con_sex_ttest_neg$statistic,2)
  ),
  "95% CI" = c(
    paste0(
      "(", 
      round(con_sex_ttest_pos$conf.int[[1]],2), 
      ", ",  
      round(con_sex_ttest_pos$conf.int[[2]],2), 
      ")", sep = ""
    ),
    paste0(
      "(", 
      round(con_sex_ttest_neg$conf.int[[1]],2),
      ", ", 
      round(con_sex_ttest_neg$conf.int[[2]],2), 
      ")", sep = ""
    )
  ),
  "df" = c(
    round(con_sex_ttest_pos$parameter,1), 
    round(con_sex_ttest_neg$parameter,1)
  ),
  "p-value" = c(
    round(con_sex_ttest_pos$p.value, 3),
    round(con_sex_ttest_neg$p.value,3)
  )
)

knitr::kable(con_sex_tab, booktabs = TRUE, caption = "Statistical test of difference: Continuous outcome and biological sex.")
```

### Figure 4.2

```{r eval=FALSE}
# scatter plot - interaction
ggplot(data = sim_data, aes(x = gen_id, y = outcome_num_pos_gid)) +
  coord_cartesian(ylim = c(0, 20)) + # ensures that the same y-axis length is used for both plots
  geom_jitter(size = 3, colour = "forestgreen") +
  labs(
    title = 'Interaction Example',
    subtitle = 'Scatter plot of continuous outcome \nand gender identity (n=30)'
    ) +
  ylab("Continuous Outcome") + xlab("Feminine - Masculine Continuum") +
  theme_classic() +
  theme(
    legend.position = 'none',
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank()
  )

# scatter plot - no interaction
ggplot(data = sim_data, aes(x = gen_id, y = outcome_num_neg)) +
  coord_cartesian(ylim = c(0, 20)) + # ensures that the same y-axis length is used for both plots
  geom_jitter(size = 3, colour = "forestgreen") +
  labs(
    title = 'No Interaction Example',
    subtitle = 'Scatter plot of continuous outcome \nand gender identity (n=30)'
    ) +
  ylab("Continuous Outcome") + xlab("Feminine - Masculine Continuum") +
  theme_classic() +
  theme(
    legend.position = 'none',
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank()
  )
```

### Figure 4.3

```{r eval=FALSE}
# 2d density plot - interaction
ggplot(data = sim_data, aes(x = gen_id, y = outcome_num_pos_gid)) + 
  geom_density_2d_filled(
    aes(fill = after_stat(level)), bins = 9, contour_var = 'ndensity'
    ) +
  scale_fill_brewer(
    palette = 16, direction = 1, 
    labels = c('Low', '', '', '','','','','', 'High')
    ) +
  guides(fill = guide_legend(
    title = 'Density of Occurences', 
    direction = 'horizontal', nrow = 1, 
    label.position = 'bottom')
    ) +
  labs(
    title = 'Interaction Example',
    subtitle = '2-D Density plot of continuous outcome \nand gender identity (n=30)'
    ) +
  ylab("Continuous Outcome") + xlab("Feminine - Masculine Continuum") +
  theme_classic() +
  theme(
    legend.position = 'none',
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank()
  ) +
  geom_blank(aes(y = 20)) + # extends y axis to ensure plots are comparable
  geom_blank(aes(y = 0))

# 2d density plot - no interaction
ggplot(data = sim_data, aes(x = gen_id, y = outcome_num_neg)) + 
  geom_density_2d_filled(
    aes(fill = after_stat(level)), bins = 9, contour_var = 'ndensity'
    ) +
  scale_fill_brewer(
    palette = 16, direction = 1, 
    labels = c('Low', '', '', '','','','','', 'High')
    ) +
  guides(fill = guide_legend(
    title = 'Density of Occurences', 
    direction = 'horizontal', nrow = 1, 
    label.position = 'bottom')
    ) +
  labs(
    title = 'No Interaction Example',
    subtitle = '2-D Density plot of continuous outcome \nand gender identity (n=30)'
    ) +
  ylab("Continuous Outcome") + xlab("Feminine - Masculine Continuum") +
  theme_classic() +
  theme(
    legend.position = 'none',
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank()
  ) +
  geom_blank(aes(y = 20)) + # extends y axis to ensure plots are comparable
  geom_blank(aes(y = 0))
```

### Table 4.5

```{r eval=FALSE}
# calculate correlations
con_gi_r_neg <- cor.test(sim_data$outcome_num_neg, sim_data$gen_id)
con_gi_r_pos <- cor.test(sim_data$outcome_num_pos_gid, sim_data$gen_id)

# output table of results
con_gi_tab <- tibble(
  "Example" = c("Interaction", "No interaction"),
  "Correlation Type" = c("Pearson's r", "Pearson's r"),
  "r" = c(
    round(con_gi_r_pos$estimate,2),
    round(con_gi_r_neg$estimate,2)
  ),
  "95% CI" = c(
    paste0(
      "(",
      round(con_gi_r_pos$conf.int[[1]],2),
      ", ",
      round(con_gi_r_pos$conf.int[[2]],2),
      ")", sep = ""
    ),
    paste0(
      "(",
      round(con_gi_r_neg$conf.int[[1]],2),
      ", ",
      round(con_gi_r_neg$conf.int[[2]],2),
      ")", sep = ""
    )
  ),
  "df" = c(
    round(con_gi_r_pos$parameter,1),
    round(con_gi_r_neg$parameter,1)
  ),
  "Significance Test" = c("t-test", "t-test"),
  "T-score" = c(
    round(con_gi_r_pos$statistic,2),
    round(con_gi_r_neg$statistic,2)
  ),
  "p-value" = c(
    round(con_gi_r_pos$p.value, 3),
    round(con_gi_r_neg$p.value,3)
  )
)

knitr::kable(con_gi_tab, booktabs = TRUE, caption = "Statistical test of difference: Continuous outcome and Gender Idenity Item from the SGBA-5.")
```

### Figure 4.4

```{r eval=FALSE}
# scatter plot - interaction
ggplot(data = sim_data, aes(x = gen_id, y = outcome_num_pos_gid)) +
  coord_cartesian(ylim = c(0, 20)) + # ensures that the same y-axis length is used for both plots
  geom_jitter(size = 3, colour = "forestgreen") +
  labs(
    title = 'Gender Identity',
    subtitle = 'Scatter plot of continuous outcome \nand gender identity (n=30)'
    ) +
  ylab("Continuous Outcome") + xlab("Feminine - Masculine Continuum") +
  theme_classic() +
  theme(
    legend.position = 'none',
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank()
  )

# scatter plot - no interaction
ggplot(data = sim_data, aes(x = gen_role, y = outcome_num_pos_gid)) +
  coord_cartesian(ylim = c(0, 20)) + # ensures that the same y-axis length is used for both plots
  geom_jitter(size = 3, colour = "forestgreen") +
  labs(
    title = 'Gendered Roles',
    subtitle = 'Scatter plot of continuous outcome \nand gendered roles (n=30)'
    ) +
  ylab("Continuous Outcome") + xlab("Feminine - Masculine Continuum") +
  theme_classic() +
  theme(
    legend.position = 'none',
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank()
  )
```

### Figure 4.5

```{r eval=FALSE}
# 2d density plot - interaction
ggplot(data = sim_data, aes(x = gen_id, y = outcome_num_pos_gid)) + 
  geom_density_2d_filled(
    aes(fill = after_stat(level)), bins = 9, contour_var = 'ndensity'
    ) +
  scale_fill_brewer(
    palette = 16, direction = 1, 
    labels = c('Low', '', '', '','','','','', 'High')
    ) +
  guides(fill = guide_legend(
    title = 'Density of Occurences', 
    direction = 'horizontal', nrow = 1, 
    label.position = 'bottom')
    ) +
  labs(
    title = 'Gender Identity',
    subtitle = '2-D Density plot of continuous outcome \nand gender identity (n=30)'
    ) +
  ylab("Continuous Outcome") + xlab("Feminine - Masculine Continuum") +
  theme_classic() +
  theme(
    legend.position = 'none',
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank()
  ) +
  geom_blank(aes(y = 20)) + # extends y axis to ensure plots are comparable
  geom_blank(aes(y = 0))

# 2d density plot - no interaction
ggplot(data = sim_data, aes(x = gen_role, y = outcome_num_pos_gid)) + 
  geom_density_2d_filled(
    aes(fill = after_stat(level)), bins = 9, contour_var = 'ndensity'
    ) +
  scale_fill_brewer(
    palette = 16, direction = 1, 
    labels = c('Low', '', '', '','','','','', 'High')
    ) +
  guides(fill = guide_legend(
    title = 'Density of Occurences', 
    direction = 'horizontal', nrow = 1, 
    label.position = 'bottom')
    ) +
  labs(
    title = 'Gendered Roles',
    subtitle = '2-D Density plot of continuous outcome \nand gendered roles (n=30)'
    ) +
  ylab("Continuous Outcome") + xlab("Feminine - Masculine Continuum") +
  theme_classic() +
  theme(
    legend.position = 'none',
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank()
  ) +
  geom_blank(aes(y = 20)) + # extends y axis to ensure plots are comparable
  geom_blank(aes(y = 0))
```

### Table 4.6

```{r eval=FALSE}
# calculate correlations
con_gi_r_pos <- cor.test(sim_data$outcome_num_pos_gid, sim_data$gen_id)
con_gr_r_pos <- cor.test(sim_data$outcome_num_pos_gid, sim_data$gen_role)

# output table of results
con_2gah_tab <- tibble(
  "Example" = c("Gender Identity", "Gendered Roles"),
  "Correlation Type" = c("Pearson's r", "Pearson's r"),
  "r" = c(
    round(con_gi_r_pos$estimate,2),
    round(con_gr_r_pos$estimate,2)
  ),
  "95% CI" = c(
    paste0(
      "(",
      round(con_gi_r_pos$conf.int[[1]],2),
      ", ",
      round(con_gi_r_pos$conf.int[[2]],2),
      ")", sep = ""
    ),
    paste0(
      "(",
      round(con_gr_r_pos$conf.int[[1]],2),
      ", ",
      round(con_gr_r_pos$conf.int[[2]],2),
      ")", sep = ""
    )
  ),
  "df" = c(
    round(con_gi_r_pos$parameter,1),
    round(con_gr_r_pos$parameter,1)
  ),
  "Significance Test" = c("t-test", "t-test"),
  "T-score" = c(
    round(con_gi_r_pos$statistic,2),
    round(con_gr_r_pos$statistic,2)
  ),
  "p-value" = c(
    round(con_gi_r_pos$p.value, 3),
    round(con_gr_r_pos$p.value,3)
  )
)

knitr::kable(con_2gah_tab, booktabs = TRUE, caption = "Statistical test of difference: Continuous outcome by Gender Idenity and Gendered Roles Items from the SGBA-5.")
```
